Stack Safety as a Security Property

### 2020-07-07 main.tex
Improved examples (haven't figured out cross-hatching though) and updated lazy definitions

A trace over a type $\TRACEELEMS$ is a nonempty, finite or infinite sequence of
$\TRACEELEMS$s. We will mostly be concerned with sequences of pairs of machine states
and observations, called machine traces and denoted $\machOT \in \MOTRACE$,
and with sequences of triples of a machine state, a policy state, and an
observation, denoted $\MPT \in \MPOTRACE$ and referred to as MP-traces. 
\rb{The way the definitions are set up, one may expect MPO, but\ldots}

@@

The ``trace-of'' operator, written \(\mach \hookrightarrow \machOT\),
coinductively relates a machine state with the trace of machine states
paired with observations produced by repeated application of step:

\judgmenttwo{\(\mach_0 \stepstoobs{\obs} \mach_1\)}{\(\mach_1 \hookrightarrow \machOT\)}
            {\(\mach_0 \hookrightarrow (\mach_0,\obs) \machOT\)}%
%
\noindent
Since the step function is total, if \(\mach \hookrightarrow \machOT\),
then \(\machOT\) must be infinite.

@@

\begin{minipage}{.4\textwidth}
\judgment{\(\neg \exists \pol_1 . \pol_0 \rightharpoonup \pol_1\)}
         {\(\mpstate{\mach_0}{\pol_0} \hookrightarrow \mpostate{\mach_0}{\pol_0}{\tau}\)}
\end{minipage}
\begin{minipage}{.55\textwidth}
\judgmentthree{\(\mach_0 \stepstoobs{\obs} \mach_1\)}
              {\(\pol_0 \rightharpoonup \pol_1\)}
              {\(\mpstate{\mach_1}{\pol_1} \hookrightarrow \machOT\)}
              {\(\mpstate{\mach_0}{\pol_0} \hookrightarrow_P \mpostate{\mach_0}{\pol_0}{\obs} \machOT\)}
\end{minipage}
\rb{Shouldn't the conclusion of the first judgment use $\hookrightarrow_P$?
  And in the second judgment, wouldn't $MO$ be $MPO$, and the third premise $\hookrightarrow_P$?}

@@

We will frequently take a prefix of the trace from an initial state up
through the first state where some condition holds on the machine state.
This can easily be implemented using \(\PUT\), and we provide special notation
for convenience.
%
Let \(f\) be a predicate on machine states. Then we define \(\mach
\hookrightarrow \machOT | f\) (read ``\(\machOT\) is the prefix of
running \(\mach\) up to \(f\)''):

\judgmenttwo{\(\mach \hookrightarrow \machOT'\)}
            {\(\PUT(f,\machOT')
              = \machOT\)}
            {\(\mach \hookrightarrow \machOT | f\)}
\noindent
And similarly for traces with policies:

@@

\begin{figure}
  \integritylazyexample
  \caption{Rolling back from Figure \ref{fig:intex}\leo{Where is this referenced?
    Shouldn't this be in the lazy part?}}
  \label{fig:intlex}
\end{figure}

@@

\begin{figure}
  \confidentialityduringexample
  \caption{Failing Trace Confidentiality by Varying Observations}
  \label{fig:confex1}
\end{figure}

\begin{figure}
  \confidentialityendexample
  \caption{Failing Trace Confidentiality at End State}
  \label{fig:confex2}
\end{figure}

\definition{Trace Confidentiality} We will say two traces $MP$ and $M$
satisfy {\em trace confidentiality} with respect to $\contour$ if:
\begin{itemize}
\item If $MP$ is finite and its final state $\mach_r$ is a valid
  return\leo{Is this ill-scoped?}, then $M$ is also finite with some final state $\mach_r'$ and
  any changes from the initial states have changed in the same way:
$$\forall \component. ~ \mach_e(\component) \not = \mach_r(\component)
  \vee \mach_e'(\component) \not = \mach_r'(\component) \rightarrow
  \mach_r(\component) = \mach_r'(\component)$$
  In addittion their observations must be equivalent:
  $$\pi_o(MP) \eqsim \pi_o(M)$$
\item If $MP$ is infinite, then $M$ is also infinite and their
  observations are equivalent:
  $$\pi_o(MP) \eqsim \pi_o(M)$$
\item If the $MP$ ends prematurely with a policy fault, then
  we require that its observations are a prefix of those of $M$:
  $$\pi_o(MP) \lesssim \pi_o(M)$$
\end{itemize}

@@

%\begin{figure}
%  \confidentialityduringexample
%  \caption{Failing Trace Confidentiality by Varying Observations}
%  \label{fig:confex1}
%\end{figure}

@@

\definition{Stack Confidentiality}
Let $\callmap$ be a call map and $\codemap$ a code map. We say that a
system satisfies {\em stack confidentiality} with respect to
$\callmap$ and $\codemap$ if, for every initial machine-policy state
pair $(\mach_0, \pol_0)$ and its induced trace $\MPT$, and every
$n$-transition $(\mach_c, \pol_c)$ and $(\mach_e, \pol_e)$ to a callee
$f$ in $\MPT$, the prefix $\MPT_{pre}$ of $\MPT$ from $(\mach_e, \pol_e)$
until the first return corresponding to $\mach_c$ (if any) satisfies
trace integrity with respect to every similarly prefixed machine trace
of every variation $\mach_e'$ with the contour at the call:
$$\forall \MPT_{pre} ~ \machOT_{pre}. ~
\mpstate{\mach_e}{\pol_e} \hookrightarrow_P \MPT_{pre} ~ | ~ \ret{\mach_c} \rightarrow$$
$$\forall \mach_e'. ~ \mach_e \approx_{\mathit{Cof}(\mach_c, f, n)} \mach_e' \wedge
\mach_e' \hookrightarrow \machOT_{pre} ~ | ~ \ret{\mach_c} \rightarrow$$
$$\mathit{conf}~\mathit{Cof}(\mach_c, f, n) ~ \MPT_{pre} ~ \machOT_{pre}$$

@@

Both the integrity and confidentiality components of local state
encapsulation concern themselves with the accessibility of data, and
may hold on a wide range of programs that violate expected control
flow. For example, if {\tt g} managed to jump in the middle of the
code of {\tt h} with its call, confidentiality and integrity would
still be satisfied. 
%
However, that is still unwanted behavior: for example, a caller (or a
callee) should not be able to bypass a password check by jumping (or
returning) in the middle of a block of code - even if such an execution
would ostensibly satisfy local state encapsulation.
%
Stack safety is traditionally associated with preventing such unwanted
flows: every jump between functions should either be a call or a
return, and each return should to the instruction after its
corresponding call.

To formally capture this aspect of stack safety, we introduce three
security properties that rely on the underlying knowledge of the
program structure (code maps, function maps, return maps, and entry
maps): {\em control separation} ensures the validity of transition
sources between functions, {\em entry integrity} ensures the validity
of call targets, and {\tt return integrity} ensures the validity of
return targets.

\definition{Control Separation}

A system enjoys {\em control separation} with regard to a function map
\(\codemap\), a call map \(\callmap\), and a return map \(\retmap\),
if for any initial state \((\mach_0, \pol_0)\) and any adjacent pair
of states \((\mach_1,\pol_1)\) and \((\mach_2,\pol_2)\) in the induced
trace from \(\mpstate{\mach_0}{\pol_0})\) whose current instruction
belongs to different functions according to the function map,
either $\mach_1$ is a valid call or a valid return:

\[ \codemap(\mach_1(\PCname)) \not = \codemap(\mach_2(\PCname)) \rightarrow
\exists n. ~ \callmap(\mach_1(\PCname)) = n \vee
\retmap(\mach_1) \]

\definition{Entry Integrity}

A system enjoys {\em entry integrity} with regard to a call map
\(\callmap\) and entry map \(\entmap\) if for any initial state
\((\mach_0, \pol_0)\) and any n-transition \((\mach_c,\pol_c)\) and
\((\mach_e, \pol_e)\) in the induced trace from
\(\mpstate{\mach_0}{\pol_0}\), $\mach_e$ is a member of the entry map:
\[\callmap(\mach_c(\PCname)) = n \rightarrow \entmap(\mach_e)\]

\definition{Return Integrity}

\newcommand*{\Unmatched}{\mathit{Unmatched}}

Return integrity captures the expected behavior of marked returns with
regard to their call points. Given a call map $\callmap$ and a return
map $\retmap$, we begin by defining a coinductive relation
$\Unmatched$ over two $\MPOTRACE$ $\MPT$ and $\MPT'$, if $\MPT'$ is a
suffix of $\MPT$ whose head is the first unmatched return in $\MPT$.

Formally:
\begin{itemize}
\item A trace that starts with a return is related to itself:

  \judgmenttwo{\(\callmap(\mach(\PCname)) = \bot\)}
              {\(\retmap(\mach(\PCname))\)}
              {\(\Unmatched ~ \mpstate{\mach}{\pol} ~ \mpstate{\mach}{\pol}\)}
  \judgmenttwo{\(\callmap(\mach(\PCname)) = \bot\)}
              {\(\retmap(\mach(\PCname))\)}
              {\(\Unmatched ~ \mpstate{\mach}{\pol}\MPT ~ \mpstate{\mach}{\pol}\MPT\)}

\item If a trace \(\MPT\) starts with a non-call, non-return state,
  its unmatched return must come later:

  \judgment{\(\callmap(\mach(\PCname)) = \bot
              \hspace{.5cm} \neg \retmap(\mach(\PCname))
              \Unmatched ~ \MPT ~ \MPT'\)}
           {\(\Unmatched ~ \mpstate{\mach}{\pol}\MPT ~ \MPT'\)}

\item Finally, if a trace starts with the call, then we must discard the first
  unmatched return to get to the real one:

  \judgmentbr{\(\callmap(\mach(\PCname)) = n \hspace{.5cm} \neg \retmap(\mach(\PCname)) \)}
             {\(\MPT = (m,p)\MPT_{\mathit{call}}\) \quad \(\Unmatched ~ \MPT_{\mathit{call}} ~ \MPT_{\mathit{matched}}\)}
             {\(\MPT_{\mathit{matched}} = \mpstate{\mach'}{\pol'} \MPT_{\mathit{tail}}\) \quad
              \(\Unmatched ~ \MPT_{\mathit{tail}} ~ \MPT_{\mathit{unmatched}}\)}
            {\(\Unmatched ~ \MPT ~ \MPT_{\mathit{unmatched}}\)}
\end{itemize}
A system enjoys {\em return integrity} with regard to a call map
\(\callmap\) and return map \(\retmap\) if for any initial state pair
\((\mach_0, \pol_0)\) and any state pair \((\mach_c, \pol_c)\)
corresponding to a call in its induced trace, if
\(\mpstate{\mach_c}{\pol_c} \hookrightarrow_P \MPT\) and \(\mach_r\)
is the first unmatched return such that for some $\pol_r$
\[ \Unmatched ~ \MPT ~ (m_r,p_r)\MPT',\]
then $\mach_r$ corresponds to a return state for $\mach_c$:
\[\ret{\mach_c}\ \mach_r\]

@@

    \definition{Observable Integrity}
      Observable integrity weakens eager integrity by allowing a returned state
      to differ from its call state at high integrity components, provided the
      observable behavior of the induced trace from the return matches that of
      an idealized state whose high integrity components do match the call
      state.

@@

      If \(\mach_e\) is an entry to a call with contour \(\contour\) and
      \(\mach_r\) its return, \(\mathit{roll}(\contour,\mach_e,\mach_r)\)
      agrees with \(\mach_e\) on every component the callee should not change,
      but with \(\mach_r\) on those components that it is permitted to change.
      So the observable behavior that follows is the idealized behavior to
      which we compare the trace from \(\mach_r\), which must prefix it (to
      account for premature halts due to policy violations.)
      \rb{Here, should the second premise use $\hookrightarrow_P$?}
      %
      \[\begin{split}
        \text{\sc ObsInt}_\contour ~ \MPT \triangleq
          & \MPT = \mpostate{\mach_e}{\pol_e}{\obs_e} \dots
            \mpostate{\mach_r}{\pol_r}{\obs_r} \Rightarrow \\
        & \mpstate{\mach_r}{\pol_r} \hookrightarrow \MPT' \Rightarrow \\
        & \mathit{roll}(\contour,\mach_e,\mach_r) \hookrightarrow \machOT' \Rightarrow \\
        & \pi_o(\MPT') \lesssim_O \pi_o(\machOT')
      \end{split}\]

@@

      A system enjoys {\em observable \rb{stack?} integrity} with regard to \(\callmap\)
      and  \(\codemap\) if for any initial state \(\mach_0\) and each
      transition with entry state \(\mpostate{\mach_e}{\pol_e}{\obs_e}\) and
      contour \(\contour\) in the induced trace from
      \(\mpstate{\mach_0}{\mathit{pinit}(\mach_0)}\), if
      \(\mpstate{\mach_e}{\pol_e} \hookrightarrow \MPT | \ret{\mach_e}\) \rb{$\hookrightarrow_P$?},
      then \(\text{\sc ObsInt}_\contour ~ \MPT\).

@@

      To return to the example in \cref{fig:confex}, the varied final state
      \(\mach_r'\) might do anything depending on the values of the variation,
      so we cannot immediately compare traces from \(\mach_r\) and
      \(\mach_r'\). We must first restore the varied values to their original
      state, while preserving differences that have occurred during
      execution.
      \rb{To me, this reads like a prologue to the definitions properly
        speaking---maybe the definition header above should be a paragraph and
        a definition header appear next? I would also split it into two
        definitions.}

@@

      The \(\mathit{restore}\) function takes a contour and four states: the
      original call state, a variant call state, and corresponding return
      states, and returns another state. The resulting state restores those
      components that are high confidentiality to match the original call,
      unless they were changed during execution:
      \[\mathit{restore}(\contour,\mach_e,\mach_e',\mach_r,\mach_r')(\component) =
        \begin{cases}
          \mach_c(\component) & \text{if } \contour(\component) = (\HIGHSEC,\_) \text{ and } \\
                  & \mach_e(\component) = \mach_r(\component) \text{ and }
                    \mach_e'(\component) = \mach_r'(\component) \\
          \mach_r'(\component) & \text{else} \\
        \end{cases}\]

      A pair of traces \(\MPT\) and \(\machOT\) starting from \(\mach_e\) \rb{with what $\pol_e$?} and
      \(\mach_e'\), respectively, with \(\mach_e \approx_\contour \mach_r'\) \rb{$\mach_e'$?},
      enjoy observable trace confidentiality with respect to \(\contour\) if
      two conditions hold:

      The two traces are observationally equivalent: \(\pi_o(\MPT) \eqsim
      \pi_o(\machOT)\).

      If \(\MPT\) is finite and ends with the state
      \(\mpostate{\mach_r}{\pol_r}{\obs_r}\), then \(\machOT\) is finite. Let
      \(\mach_r'\) be the final state of \(\machOT\). Then the induced traces
      \(\mpstate{\mach_r}{\pol_r} \hookrightarrow \MPT'\) \rb{$\hookrightarrow_P$?} and
      \(\mathit{restore}(\contour,\mach_e,\mach_e',\mach_r,\mach_r')
      \hookrightarrow \machOT'\) are observationally prefixed,
      \(\pi_o(\MPT') \lesssim \pi_o(\machOT')\).

      We write this \(\text{\sc ObsConf}_\contour ~ \MPT\).
      \rb{What about $\machOT$? Ditto for use in the definition of observable stack confidentiality below.}

@@

      From observable trace confidentiality we construct {\em observable stack
      confidentiality}. A system enjoys {\em observable stack confidentiality}
      with regard to \(\callmap\) and \(\codemap\) if for any initial state
      \(\mach_0\) and each transition with entry state
      \(\mpostate{\mach_e}{\pol_e}{\obs_e}\) and contour \(\contour\) in the
      induced trace from \(\mpstate{\mach_0}{\mathit{pinit}(\mach_0)}\), if
      \(\mpstate{\mach_e}{\pol_e} \hookrightarrow \MPT | \ret{\mach_e}\),
      then \(\text{\sc ObsConf}_\contour ~ \MPT\).

    \definition{Observable Stack Safety}
      A system enjoys {\em observable stack safety} with regard to a call map
      and a code map if it enjoys both observable \rb{stack?} integrity and observable
      \rb{stack?} confidentiality with regard to them.

>>>>

A trace over a type $\TRACEELEMS$ is a nonempty, finite or infinite sequence of
$\TRACEELEMS$s. We will mostly be concerned with sequences of pairs of machine states
and observations, called machine traces and denoted $\machT \in \MOTRACE$,
and with sequences of triples of a machine state, a policy state, and an
observation, denoted $\MPT \in \MPOTRACE$ and referred to as MP-traces. 
\rb{The way the definitions are set up, one may expect MPO, but\ldots}

@@

The ``trace-of'' operator, written \(\mach \hookrightarrow \machT\),
coinductively relates a machine state with the trace of machine states
paired with observations produced by repeated application of step:

\judgmenttwo{\(\mach_0 \stepstoobs{\obs} \mach_1\)}{\(\mach_1 \hookrightarrow \machT\)}
            {\(\mach_0 \hookrightarrow (\mach_0,\obs) \machT\)}%
%
\noindent
Since the step function is total, if \(\mach \hookrightarrow \machT\),
then \(\machT\) must be infinite.

@@

\begin{minipage}{.4\textwidth}
\judgment{\(\neg \exists \pol_1 . \pol_0 \rightharpoonup \pol_1\)}
         {\(\mpstate{\mach_0}{\pol_0} \hookrightarrow \mpostate{\mach_0}{\pol_0}{\tau}\)}
\end{minipage}
\begin{minipage}{.55\textwidth}
\judgmentthree{\(\mach_0 \stepstoobs{\obs} \mach_1\)}
              {\(\pol_0 \rightharpoonup \pol_1\)}
              {\(\mpstate{\mach_1}{\pol_1} \hookrightarrow \machT\)}
              {\(\mpstate{\mach_0}{\pol_0} \hookrightarrow_P \mpostate{\mach_0}{\pol_0}{\obs} \machT\)}
\end{minipage}
\rb{Shouldn't the conclusion of the first judgment use $\hookrightarrow_P$?
  And in the second judgment, wouldn't $MO$ be $MPO$, and the third premise $\hookrightarrow_P$?}

@@

We will frequently take a prefix of the trace from an initial state up
through the first state where some condition holds on the machine state.
This can easily be implemented using \(\PUT\), and we provide special notation
for convenience.
%
Let \(f\) be a predicate on machine states. Then we define \(\mach
\hookrightarrow \machT | f\) (read ``\(\machT\) is the prefix of
running \(\mach\) up to \(f\)''):

\judgmenttwo{\(\mach \hookrightarrow \machT'\)}
            {\(\PUT(f,\machT')
              = \machT\)}
            {\(\mach \hookrightarrow \machT | f\)}
\noindent
And similarly for traces with policies:

@@

@@

\definition{Trace Confidentiality} We will say two traces $MP$ and $M$
satisfy {\em trace confidentiality} with respect to $\contour$ if:
\begin{itemize}
\item If $\MPT$ is finite and its final state $\mach_r$ is a valid
  return\leo{Is this ill-scoped?}, then $\machT$ is also finite with some final state $\mach_r'$ and
  any changes from the initial states have changed in the same way:
$$\forall \component. ~ \mach_e(\component) \not = \mach_r(\component)
  \vee \mach_e'(\component) \not = \mach_r'(\component) \rightarrow
  \mach_r(\component) = \mach_r'(\component)$$
  In addittion their observations must be equivalent:
  $$\pi_o(\MPT) \eqsim \pi_o(\machT)$$
\item If $\MPT$ is infinite, then $\machT$ is also infinite and their
  observations are equivalent:
  $$\pi_o(\MPT) \eqsim \pi_o(\machT)$$
\item If the $\MPT$ ends prematurely with a policy fault, then
  we require that its observations are a prefix of those of $\machT$:
  $$\pi_o(\MPT) \lesssim \pi_o(\machT)$$
\end{itemize}

@@

@@

\definition{Stack Confidentiality}
Let $\callmap$ be a call map and $\codemap$ a code map. We say that a
system satisfies {\em stack confidentiality} with respect to
$\callmap$ and $\codemap$ if, for every initial machine-policy state
pair $(\mach_0, \pol_0)$ and its induced trace $\MPT$, and every
$n$-transition $(\mach_c, \pol_c)$ and $(\mach_e, \pol_e)$ to a callee
$f$ in $\MPT$, the prefix $\MPT_{pre}$ of $\MPT$ from $(\mach_e, \pol_e)$
until the first return corresponding to $\mach_c$ (if any) satisfies
trace integrity with respect to every similarly prefixed machine trace
of every variation $\mach_e'$ with the contour at the call:
$$\forall \MPT_{pre} ~ \machT_{pre}. ~
\mpstate{\mach_e}{\pol_e} \hookrightarrow_P \MPT_{pre} ~ | ~ \ret{\mach_c} \rightarrow$$
$$\forall \mach_e'. ~ \mach_e \approx_{\mathit{Cof}(\mach_c, f, n)} \mach_e' \wedge
\mach_e' \hookrightarrow \machT_{pre} ~ | ~ \ret{\mach_c} \rightarrow$$
$$\mathit{conf}~\mathit{Cof}(\mach_c, f, n) ~ \MPT_{pre} ~ \machT_{pre}$$

@@

Our integrity and confidentiality properties concern themselves with
data, and may hold on a wide range of programs that violate expected
control flow.  But well-bracketed control flow prevents this style of
attack by guaranteeing that every jump between functions is either a
call or a return, and each return jumps to the instruction after a
corresponding call.

\leo{Also dumping in relevant wbcf discussion part. TODO: merge}
    Some forms of security rely on protected control flow. In a classic
    example, a system call that launches a missile might be gated behind code
    that checks a password. A piece of malicious code can jump into the middle
    of the sequence and execute the system call without the appropriate password,
    and still obey integrity if the malicious code never returns to its caller.
    Integrity here protects data, not privileges. But such a jump does violate
    eager stack confidentiality if the attacker jumps beyond its own function's
    instructions without performing a designated call or returning to an
    appropriate site.

    A jump to a function's own code does not violate either, even if done using
    nefarious means such as return-oriented programming (ROP). Our model would
    permit such a jump within the function, so privilege is not elevated by
    permitting ROP in this case.

    But, our policies do enforce orthogonal control flow properties that
    protect from calls that enter outside of valid entry points and from all
    invalid returns, even if they would not escalate privilege. Most notably
    {\em well-bracketed control flow}, below.

\definition{Control Separation}
A system enjoys {\em control separation} with regard to a code map
\(\codemap\), a call map \(\callmap\), and a return map \(\retmap\) if
for any initial state \(\mach_0\) and any adjacent pair of states
\(\mach_1\) and \(\mach_2\) in the induced trace from
\(\mpstate{\mach_0}{\pinit(\mach_0)}\), if
\(\codemap(\mach_1(\PCname)) \not = \codemap(\mach_2)\), then either
\(\callmap(\mach_1(\PCname)) = n\) for some \(n\), or
\(\retmap(\mach_1)\).

\definition{Entry Integrity}
A system enjoys {\em entry integrity} with regard to a call map
\(\callmap\) and entry map \(\entmap\) if for any initial state
\(\mach_0\) and any adjacent pair of states \(\mach_c\) and
\(\mach_e\) in the induced trace from
\(\mpstate{\mach_0}{\pinit(\mach_0)}\), if
\(\callmap(\mach_c(\PCname)) = n\) then \(\entmap(\mach_e)\).

\definition{Return Integrity}
Return integrity captures the expected behavior of marked returns with
regard to their call points. We begin by defining a coinductive
relation \(\mathit{Unmatched}\ \callmap\ \retmap\ \MPT_1
\MPT_2\). Given a call map \(\callmap\) and return map \(\retmap\),
\(\MPT\) is related to \(\MPT'\) if \(\MPT'\) is a suffix of \(\MPT\)
whose head is the first unmatched return in \(\MPT\). So if \(\MPT\)
starts with a return, it is related to itself:

  \judgmenttwo{\(\callmap(\mach(\PCname)) = \bot\)}
           {\(\retmap(\mach(\PCname))\)}
      {\(\mathit{Unmatched}\ \callmap\ \retmap\ \mpstate{\mach}{\pol}\
        \mpstate{\mach}{\pol}\)}
  \judgmenttwo{\(\callmap(\mach(\PCname)) = \bot\)}
              {\(\retmap(\mach(\PCname))\)}
      {\(\mathit{Unmatched}\ \callmap\ \retmap\ \mpstate{\mach}{\pol}\MPT\
              \mpstate{\mach}{\pol}\MPT\)}

If \(\MPT\) starts with a non-call, non-return state, its unmatched
return must come later:

  \judgment{\(\callmap(\mach(\PCname)) = \bot
              \hspace{.5cm} \neg \retmap(\mach(\PCname))

              \mathit{Unmatched}\ \callmap\ \retmap\ \MPT\ \MPT'\)}
           {\(\mathit{Unmatched}\ \callmap\ \retmap\
            \mpstate{\mach}{\pol}\MPT\ \MPT'\)}

And most intricately, if \(\MPT\) starts with a call, we must find the
return that matches it, which will be the unmatched return once we
step past the call. Then the first unmatched return beyond it is the
true unmatched return.

    \judgment{\(\callmap(\mach(\PCname)) = n
              \hspace{.5cm} \neg \retmap(\mach(\PCname))\)

              \(\MPT = \mpstate{\mach}{\pol} \MPT_{\mathit{call}}\)

              \(\mathit{Unmatched}\ \callmap\ \retmap\ \MPT_{\mathit{call}}\ \MPT_{\mathit{matched}}\)

              \(\MPT_{\mathit{matched}} = \mpstate{\mach'}{\pol'} \MPT_{\mathit{tail}}\)

              \(\mathit{Unmatched}\ \callmap\ \retmap\ \MPT_{\mathit{tail}}\ \MPT_{\mathit{unmatched}}\)}
            {\(\mathit{Unmatched}\ \callmap\ \retmap\ \MPT\ \MPT_{\mathit{unmatched}}\)}

A system enjoys {\em return integrity} with regard to a call map
\(\callmap\) and return map \(\retmap\) if for any initial state
\(\mach_0\) and any call state and policy state \(\mach_c\) and
\(\pol_c\) in the induced trace from
\(\mpstate{\mach_0}{\pinit(\mach_0)}\), if \(\mpstate{\mach_c}{\pol_c}
\hookrightarrow_P \MPT\) and \(\mach_r\) is the first unmatched
return, with \(\mathit{Unmatched}\ \callmap\ \retmap\ \MPT \ \MPT'\)
and \(\mach_r\) the first machine state of \(\MPT'\), then
\(\ret{\mach_c}\ \mach_r\).

@@

    \paragraph{Rolling Back to Idealized State}
      Observable integrity will weaken eager integrity by allowing a returned
      state to differ from its call state at high integrity components,
      provided the observable behavior of the induced trace from the return
      matches that of an idealized state whose high integrity components do
      match the call state.

@@

      If \(\mach_e\) is an entry to a call with contour \(\contour\) and
      \(\mach_r\) its return, \(\mathit{roll}(\contour,\mach_e,\mach_r)\)
      agrees with \(\mach_e\) on every component the callee should not change,
      but with \(\mach_r\) on those components that it is permitted to change.
      So the observable behavior that follows is the idealized behavior to
      which we compare the trace from \(\mach_r\), which must prefix it (to
      account for premature halts due to policy violations.)

      Now we can define a version of trace integrity that compares the trace
      from a returned state to that from its idealized counterpart.

    \definition{Observable Trace Integrity}

      An MP-Trace enjoys {\em observable trace integrity} with respect to
      some contour \(\contour\) if its final state (if any) has observable
      behavior that prefixes that of its idealized version, constructed by
      \(\mathit{roll}\):

      \[\begin{split}
        \text{\sc ObsInt}_\contour ~ \MPT \triangleq
        & \mpostate{\mach_e}{\pol_e}{\obs_e} = \head(\MPT) \\
        & \mpostate{\mach_r}{\pol_r}{\obs_r} = \last(\MPT) \Rightarrow \\
        & \mpstate{\mach_r}{\pol_r} \hookrightarrow_P \MPT' \Rightarrow \\
        & \mathit{roll}(\contour,\mach_e,\mach_r) \hookrightarrow \machT' 
          \Rightarrow \\
        & \pi_o(\MPT') \lesssim_O \pi_o(\machT')
      \end{split}\]

@@

      A system enjoys {\em observable stack integrity} with regard to
      \(\callmap\) and \(\codemap\) if for any initial state \(\mach_0\) and
      each transition with entry state \(\mpostate{\mach_e}{\pol_e}{\obs_e}\)
      and contour \(\contour\) in the induced trace from
      \(\mpstate{\mach_0}{\mathit{pinit}(\mach_0)}\), if
      \(\mpstate{\mach_e}{\pol_e} \hookrightarrow_P \MPT | \ret{\mach_e}\),
      then \(\text{\sc ObsInt}_\contour ~ \MPT\).

    \paragraph{Restoring Varied States}

@@

      To return to the example in \cref{fig:confex}, the varied final state
      \(\mach_r'\) might do anything depending on the values of the variation,
      so we cannot immediately compare traces from \(\mach_r\) and
      \(\mach_r'\). We must first restore the varied values to their original
      state, while preserving differences that have occurred during
      execution.
      \rb{To me, this reads like a prologue to the definitions properly
        speaking---maybe the definition header above should be a paragraph and
        a definition header appear next? I would also split it into two
        definitions.}
      \sna{Definitely better as a prologue. Where would you split it?}

@@

      The \(\mathit{restore}\) function takes a contour and four states: the
      original call state, a variant call state, and corresponding return
      states, and returns another state. The resulting state restores those
      components that are high confidentiality to match the original call,
      unless they were changed during execution:
      \[\mathit{restore}(\contour,\mach_e,\mach_e',\mach_r,\mach_r')
        (\component) =
        \begin{cases}
          \mach_c(\component) & \text{if } \contour(\component) = (\HIGHSEC,\_)
            \text{ and } \\
          & \mach_e(\component) = \mach_r(\component) \text{ and }
            \mach_e'(\component) = \mach_r'(\component) \\
          \mach_r'(\component) & \text{else} \\
        \end{cases}\]

      Now we can describe a trace property that extends trace confidentiality.

      A pair of traces \(\MPT\) and \(\machT\) starting from
      \(\mpstate{\mach_e}{\pol_e}\) and \(\mach_e'\), respectively, with
      \(\mach_e \approx_\contour \mach_e'\), enjoy observable trace
      confidentiality with respect to \(\contour\) if two conditions hold:

      The two traces are observationally equivalent: \(\pi_o(\MPT) \eqsim
      \pi_o(\machT)\).

      If \(\MPT\) is finite and ends with the state
      \(\mpostate{\mach_r}{\pol_r}{\obs_r}\), then \(\machT\) is finite. Let
      \(\mach_r' = \last(\machT)\). Then the induced traces
      \(\mpstate{\mach_r}{\pol_r} \hookrightarrow_P \MPT'\) and
      \(\mathit{restore}(\contour,\mach_e,\mach_e',\mach_r,\mach_r')
      \hookrightarrow \machT'\) are observationally prefixed,
      \(\pi_o(\MPT') \lesssim \pi_o(\machT')\).

      We write this \(\text{\sc ObsConf}_\contour ~ \MPT ~ \machT\).

@@

      From observable trace confidentiality we construct {\em observable stack
      confidentiality}. A system enjoys {\em observable stack confidentiality}
      with regard to \(\callmap\) and \(\codemap\) if for any initial state
      \(\mach_0\) and each transition with entry state
      \(\mpostate{\mach_e}{\pol_e}{\obs_e}\) and contour \(\contour\) in the
      induced trace from \(\mpstate{\mach_0}{\mathit{pinit}(\mach_0)}\), if
      \(\mpstate{\mach_e}{\pol_e} \hookrightarrow \MPT | \ret{\mach_e}\),
      then \(\text{\sc ObsConf}_\contour ~ \MPT ~ \machT\).

    \definition{Observable Stack Safety}
      A system enjoys {\em observable stack safety} with regard to a call map
      and a code map if it enjoys both observable stack integrity and
      observable stack confidentiality with regard to them.
